---
title: "Reproducible Research Course Project 1"
author: "Iosvany Moya"
date: "16 de noviembre de 2016"
output: html_document
---

### Loading and preprocessing the data
1- Code for reading in the dataset and/or processing the data
```{r setup}
library(ggplot2)
actdat <- read.csv("activity.csv", na.strings = "NA", colClasses = c("numeric","Date", "numeric"))
str(actdat)
```

### What is mean total number of steps taken per day?

2- total number of steps taken per day
```{r totals per day}
actstepsum <- tapply(actdat$steps, actdat$date, sum, na.rm=TRUE)
qplot(actstepsum, geom="histogram", binwidth=500)
```

3- Mean and median number of steps taken each day
```{r mean and median per day}
mean(actstepsum)
median(actstepsum)
```

### What is the average daily activity pattern?
4- Time series plot of the average number of steps taken
```{r average daily activity pattern}
actstepavg <- aggregate(x=list(meanSteps=actdat$steps), by=list(interval=actdat$interval), FUN=mean, na.rm=TRUE)
ggplot(data=actstepavg, aes(x=interval, y=meanSteps)) + geom_line()

```
5- The 5-minute interval that, on average, contains the maximum number of steps
```{r max interval}
actstepavg[which.max(actstepavg$meanSteps),'interval']
```

### Imputing missing values
6- Code to describe and show a strategy for imputing missing data

In a separate copy of the dataset, loop the steps sequence replacing the NA values with the median of the observed steps for that interval. 

```{r handle missing values}
length(which(is.na(actdat$steps)))
actstepmed <- tapply(actdat$steps, actdat$interval, median, na.rm=TRUE)
actdat_withoutna <- actdat
for (i in 1:nrow(actdat_withoutna))
{
  if (is.na(actdat_withoutna$steps[i]))
  {
    actdat_withoutna$steps[i] = sum(actstepmed[as.character(actdat_withoutna$interval[i])] )
  }
}
```

7- Histogram of the total number of steps taken each day after missing values are imputed
```{r totals per day after missing handled}
actstepsum_withoutna <- tapply(actdat_withoutna$steps, actdat_withoutna$date, sum, na.rm=TRUE)
qplot(actstepsum_withoutna, geom="histogram", binwidth=500)
```

8- Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r difference between weekday and weekend }
actstepavg <- aggregate(x=list(meanSteps=actdat$steps), by=list(interval=actdat$interval, wday=ifelse(as.POSIXlt(actdat$date)$wday<5,"weekday","weekend")), FUN=mean, na.rm=TRUE)
ggplot(data=actstepavg, aes(x=interval, y=meanSteps)) + geom_line() + facet_wrap(~ wday, ncol=1, nrow = 2)
```
